---
title: "Deployment Tutorial"
author: "Adam Rydelek"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Deployment Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = FALSE,
  comment = "#>",
  warning = FALSE,
  message = FALSE,
  eval = FALSE
)
```

# Setup dependencies

Firstly, install/update all the necessary dependencies. It is crucial that you use **github development version of plumber** in order to deploy the API to the cloud. For local use only the CRAN version is sufficient.

```{r eval = FALSE}
# install plumber from github
devtools::install_github("trestletech/plumber")
# update main dependencies
install.packages("ingredients")
install.packages("iBreakDown")
install.packages("readr")
install.packages("whisker")
# packages for explainer objects
install.packages("DALEX")
# install packages for the used model
install.packages("randomForest")
```

# Deploy the explainer locally

```{r}
library("xai2cloud")
library("DALEX")
library("randomForest")

# Load data
titanic <- na.omit(DALEX::titanic)
# Create a random forest model
model_titanic_rf <- randomForest(survived == "yes" ~ gender + age + class + embarked +
                                   fare + sibsp + parch,  data = titanic)
# Create an DALEX explainer
explain_titanic_rf <- DALEX::explain(model_titanic_rf, 
                      data = titanic[,-9],
                      y = titanic$survived == "yes", 
                      label = "Random Forest v7",
                      colorize = FALSE)
# Deploy the explainer
deploy_explainer(explain_titanic_rf, model_package = "randomForest", title="Vignette test", port=8080)
```

# Deploy the explainer to DigitalOcean

In order to deploy the explainer to the cloud using DigitalOcean's droplets you need an DigitalOcean's account and a droplet with R version >=3.5 and corresponding packages. In order to setup the droplet properly visit the [README section on github](https://github.com/Adamoso/xai2cloud).

Assuming the guide is complete and your droplet works, let's deploy it.
```{r eval=FALSE}
# First check whether your droplet is setup correctly by using analogsea package
library(analogsea)
analogsea::droplets()
# If the setup is correct after your droplet's name there is an ID.
# We will use the explainer from the previous, local example
# Deploy it to your new droplet
# Put your droplet's ID in parameter 'droplet'
deploy_explainer(explain_titanic_rf, model_package = "randomForest", title="Vignette test", droplet=185232162, port=8080)
# Your explainer is ready at: http://your_droplets_ip/explain_titanic_rf/__swagger__/
# You can deploy multiple explainers to the same droplet, just use different names and ports
# If you wish to delete the explainer from your droplet, use:
plumber::do_remove_api(droplet = 185232162, path = "explain_titanic_rf", delete = TRUE)
```

